Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-13 2017-Xudong-SMT/pNetZ3paper.tex
Add algorithm of combining
See in pNetZ3paper.tex.

%\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{algorithm}[theorem]{Algorithm}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{example}[theorem]{Example}
%\newtheorem{problem}[theorem]{Problem}
%\newtheorem{proof}[theorem]{Proof}

% Macros for the SOS rules and proof trees:
%\newcommand\openrule[2]{\redinfer{#1}{#2}}
\newcommand\openrule[2]{\inferrule*[myfraction=\reddottedrule,center]{#1}{#2}}
%\newcommand\openrule[2]{\inferrule*{#1}{#2}}
%\newcommand\ostate[1]{\triangleleft{\;#1\;}\triangleright}
\newcommand\ostate[1]{\triangleleft{#1}\triangleright}
\newcommand{\sm}[1]{\mbox{\boldmath\small #1}}

@@

\begin{algorithm}[Operational Semantics Generation Algorithm of Open pNets]
Open transitions satisfying two rules:
The rule for pLTSs (Tr1) and the rule deal with pNet nodes (Tr2).
Tr2 uses Tr1 and Tr2 recursively if there are subnets of the pNet.
So the structure of the open transitions and subnets' open transitions is like a deduction tree constructively "prove" the open transition.
To generate the list of possible open transitions for the pNet, we build all the possible deduction trees from the given start global state according to these two rules.

@@

\end{algorithm}

>>>>

%\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{alg}[theorem]{Algorithm}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{example}[theorem]{Example}
%\newtheorem{problem}[theorem]{Problem}
%\newtheorem{proof}[theorem]{Proof}

% Macros for the SOS rules and proof trees:
%\newcommand\openrule[2]{\redinfer{#1}{#2}}
\newcommand\openrule[2]{\inferrule*[myfraction=\reddottedrule,center]{#1}{#2}}
%\newcommand\openrule[2]{\inferrule*{#1}{#2}}
%\newcommand\ostate[1]{\triangleleft{\;#1\;}\triangleright}
\newcommand\ostate[1]{\triangleleft{#1}\triangleright}
\newcommand{\sm}[1]{\mbox{\boldmath\small #1}}
\usepackage{algorithm} 
\usepackage{algorithmicx} 
\usepackage{algpseudocode}  
\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

\begin{algorithm}
\caption{Operational Semantics Generation Algorithm of Open pNets} 
\begin{algorithmic}[1]

\Require 
\Ensure

\State \Return

\end{algorithmic} 
\end{algorithm}

%Combining is to generate all the possible matchings of the subnets' OTs (open transitions). The result list of the matched tuples called *combination*.
% 1. Initialize the result list of OT tuples.
% 2. Get one list of OTs. It's same as get OTs of one subnet.
% 3. Add *null* into the list, it means this subnet does not work this time.
% 4. Combine the rest subnets' OTs. Get the combination of the rest OTs.
% 5. If there are OTs of the chosen list not be chosen, choose one OT.
%      1. If there are tuples of the combination not be chosen, choose one tuple.
%          1. Add the chosen OT into the tuple.
%          2. Add the tuple into the result list, then do the recursion.
% 6. Return the result list.
\begin{algorithm}
\caption{Combining}
\begin{algorithmic}[1]

\Require List $TR$ of result open transition lists from the subnets. 
\Ensure All the possible combinations of open transitions.
\State Initial an empty combination list $C$;
\State Extract a list of open transitions $L$ from $TR$;
\State Insert $null$ into $L$;
\State Get the combinations $C'$ of the $TR$;
\For{each $ot \in L$}
	\For{each $tuple \in C'$}
		\State Add $ot$ into $tuple$;
		\State Add $tuple$ into $C$;
	\EndFor
\EndFor 
\State \Return $C$;

\end{algorithmic}  
\end{algorithm}

% Mixing is to match the combination of the subnets' open transitions, hole behaviors and result action with the SV (synchronization vector) to generate the possible predicates of the OT (open transition). At the same time, other parameters of the OT (global state, subnets' transitions, result action...) are also generated. Then the possible OTs of the pNet can be achieved. 
% 1. Initialize the combination through the method *combineOpenTransitions( )*.
% 2. Initialize the result list.
% 3. Get the number of subnets and holes. They are used to decide how many element of the SV should be matched with them.
% 4. For all tuples of the combination.
%      1. Invoke the *clone( )* method to generate the fresh SV.
%      2. Match the elements of the tuple with the elements of the SV. If there is a *null* matched with a *not null* action, filter this matching. Add the result expression and the predicate of the subnets into the predicate. Generate the target global state correspondingly.
%      3. Match the hole behaviors with the elements of the SV. The hole behavior could be *null*. Add the result expression into the predicate.
%      4. Match the result action with the result action of SV. Add the result expression into the predicate.
%      5. Add the predicate into the OT. Store the OT in the result list.  
% 5. Return the result list of all the possible OTs.
\begin{algorithm}
\caption{Matching}
\begin{algorithmic}[1]

\Require 
\Ensure

\State \Return

\end{algorithmic} 
\end{algorithm}

\begin{alg}[Operational Semantics Generation Algorithm of Open pNets]
Open transitions satisfying two rules:
The rule for pLTSs (Tr1) and the rule deal with pNet nodes (Tr2).
Tr2 uses Tr1 and Tr2 recursively if there are subnets of the pNet.
So the structure of the open transitions and subnets' open transitions is like a deduction tree constructively "prove" the open transition.
To generate the list of possible open transitions for the pNet, we build all the possible deduction trees from the given start global state according to these two rules.

@@

\end{alg}
